Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/paper.tex
Resolve most of the bibliography
Improve plots and multiple small changes
edits
pass over evaluation
pass over related work
added abstract

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{stmaryrd}
\usepackage{booktabs} % for professional tables
\usepackage{paralist}
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{amsmath}

@@

\begin{abstract}
  Let's write the abstract at the end
\end{abstract}

@@

\input{introduction}
\input{approach}
\input{impl}
\input{evaluation}
\input{related_work}
\input{discussion}
\input{conclusion}

\appendix
\input{appendix}

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{OpenML2013}

\bibliography{custom}
\bibliographystyle{icml2018}

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{stmaryrd}
\usepackage{booktabs} % for professional tables
\usepackage{paralist}

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{amsmath}

@@

\begin{abstract}
As neural networks are being increasingly deployed in 
different applications and on different hardware, it has
become increasingly important to optimize inference time
and model size along with model accuracy.
Most current work optimizes model size, model accuracy and
inference time in different stages and results in suboptimal
results at the cost of computational inefficiency.
In this work, we propose a new techique called ShrinkNets that
optimizes all three of these metrics simultaneously by learning
optimal network size at training time.
Specifically our technique presents a new method to simultaneously optimize network size and model performance by neuron-level pruning.
Neuron-level pruning not only produces much smaller 
networks for a given accuracy threshold but also produces
dense weight matrices that are efficient at inference time.
By applying our technique to a variety of models with both convolutional and fully connected layers, we show that ShrinkNets can reduce XXX by YYY and ZZZ by AAA in only BBB amount of time.

\end{abstract}

@@

\input{introduction}
\input{related_work}
\input{approach}
\input{impl}
\input{evaluation}
%\input{discussion}
\input{conclusion}

\appendix
\input{appendix}
\FloatBarrier

\clearpage

\bibliographystyle{icml2018}
\bibliography{custom,general}
